\documentclass[a4paper,12pt]{article}

\include{cv-commands}

\begin{document}

\setmainfont

%% No hyphenation
%% \hyphenchar\font=-1

%\par\vspace{25mm}

\header
%\addvspace{5mm}
{R J Karthick Raj}
{Project Manager- Cloud}
{Age: 32 years old\\
Email: bablaaa@gmail.com\\
Tel: \smcp{(+91) 9600062523}}
\newline
\newline
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{resumesummary}{Professional Profile}
\begin{itemize}      
  \item Started my career in IT as Test Engineer, involving in testing of web based applications.
  \item 2 years of experience in QA/Testing (black box) of products on Virtualization and Cloud Computing platform.
  \item Currently working as a Project Manager, Managing a 4 member Development team and a 3 member tesing team.
  \item My assignment here is to oversee the development, testing, deployment, and support of the products based on CLOUD COMPUTING (PaaS/IaaS). 
\newline
\end{itemize}
\end{resumesummary}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{resumesummary}{Summary of Specialities}
\begin{itemize}
  \item Assessment of feasibility.
  \item Accounting for all technical and non-technical tasks, collecting realistic estimates for each.
  \item Work closely with Account Management, Sales professionals, Engineering, Product development \& Customer Care to resolve technical issues that arise during customer trials or integration.
  \item Build the link between technology and business impact, with strong understanding of business processes and operations.
  \item Project Plan for development and deployment.
  \item Business requirements, Use cases, Functional specifications.
  \item Develop \& identify Functional \& Non-Functional testing methodologies, tools for IaaS cloud testing.
%  \item Develop \& identify Functional \& Non-Functional testing methodologies, tools for IaaS cloud testing.
  \item IaaS Cloud Computing, Virtualization, Network \& Storage virtualization.
  \item Experience in testing Cloud services and applications (PaaS/IaaS) and their integration with the third party apps.
%  \item Strong skills in Test case preparation, Execution \& Reporting, test reports generation and design test scenarios.
  \item Proficient in all cycles of test life cycle from test planning to defect tracking and managing defect lifecycle.
%  \item Developing and Maintaining Test Scripts, analyzing bugs and interacting with development team members in fixing the defects.
  \item Good communication and interpersonal skills with strong knowledge of Web and Product Application testing on cloud platform.
  \item Linux, Mac OSX, MySQL, Python.
  \item SVN, Redmine, Bugzilla.
\newline
\end{itemize}
\end{resumesummary}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{resumeblock}{Formation}
\newline
\resumeitem{2005-2007}\newline{M.Phil in Management from Madurai Kamaraj University(DE), Madurai.}\\
\newline
\resumeitem{2003-2005}\newline{MLM from Madurai Kamaraj University(DE), Madurai.}\\ 
\newline
\resumeitem{2001–2003}\newline{MBA from Sourashtra College, Madurai Kamaraj University, Madurai.} \\
\newline
\resumeitem{1998-2001}\newline{B.sc Computer Science from The American College, Madurai.} 
\largeskip
\end{resumeblock}

\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{resumeblock}{Professional Experience}

\resumeitem{Since March 2011}{Project Manager - Cloud, at K7 Computing Pvt Limited.\vspace{0mm}
  \begin{itemize} \itemsep0pt \parskip0pt \parsep0pt
    \item Work as a functional consultant between IT and business.
    \item Build and maintain confidence of colleagues and customers.
    \item Maintain current knowledge of the entire K7 Cloud’s product line.
    \item Worked with key stakeholders to develop priorities, define requirements, recommend solutions, construct and implement application solutions and report status for application system changes.
    \item Develop RACI matrix and identify gaps/overlaps.
    \item Understand the Business Requirement Document (BRD) which is initiated by the Product Council.
    \item Preparation of Functional Requirements with Product council. 
    \item Review, analyze and evaluated business systems and user needs.
    \item Worked with key stakeholders to develop priorities, define requirements and report status for application system changes.
    \item Interfaced with business users and other IT groups  for communicating user requirements, resolving application problems and implementing process improvements.
    \item Define Objectives for QA and UAT. 
    \item define roles and responsibilities for all team members during each phase of the product launch process.
  \end{itemize} 
\shortskip

\resumeitem{Feb 2009 - Feb 2011}{QA Lead at K7 Computing Private Limited, Chennai.\vspace{0mm}
%\resumeitem{Since Feb 2012}{Tech Lead at K7 Computing Private Limited, Chennai.\vspace{0mm}
  \begin{itemize} \itemsep0pt \parskip0pt \parsep0pt
    \item Requirements gathering and analyzing the Requirements.
    \item Create Functional Test Plans and Scenarios.
    \item Prepared Use Cases based on the Functional Requirements prepared by product council. 
    \item Involved in the creation of functional test cases, managing the UAT and functional testing of the UI before delivering it to the product council. 
    \item 
  \end{itemize}}
\shortskip

\resumeitem{Oct 2005 - Dec 2008}{Test Engineer at Infolink Software Solutions, Chennai/Bangalore.\vspace{0mm}
  \begin{itemize} \itemsep0pt \parskip0pt \parsep0pt
    \item Performed different types of testing like Functional Testing, and Smoke Testing.
    \item Involved in Executing Test cases for Functionality, integration and System Testing and preparation of test report.
    \item Reported defects found during test cycles and retest fixed in Bug Tracking System and Tracked defects using bug-tracking tool.
    \item Understanding the Test Plans and Involved in the preparation of test report.
  \end{itemize}}
\shortskip

\resumeitem{Jul 2003 - Aug 2005}{Senior Executive – Business Development at Lexicon Training Academy, Madurai.}%\vspace{0mm}
\newline
\largeskip
\end{resumeblock}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{resumeblock}{Projects}

\resumeitem{StackIron,\\ IaaS, Hypervisor Manager}{StackIron is a virtualization platform. StackIron provides a unified interface to manage all opensource hypervisors. A pure python implementation for which we developed our own development framework and billing solution. It comes integrated with third party billing solutions like WHMCS as well. All basic functionalities like backup, templatization, migration, SAN and local storage management work seamlessly across all hypervisors. StackIron provides fine grained user control and allows various levels of user configurations at runtime. StackIron has an optional VLAN and bonding functionality along with Basic Firewall and traffic controlling.}
\largeskip

\resumeitem{K7 Tracker,\\ Laptop Recovery Software}{K7 Tracker is an invisible software security application that traces the location of missing laptops for recovery. K7 Tracker is a light weight application that will help you track and 
ﬁnd your device if it ever gets stolen. It works on MAC and Linux machines. This tracking system send, over the Internet, updates regarding the current location of the device to a remotely administered repository. If the device is lost or stolen, but maintains Internet connectivity and unmodified software, the tracking system can keep tabs on the current whereabouts of the device. k7tracker.com is the device management portal, From where you can manage all your devices, 
configure and track them all from a single place.}
\largeskip

\resumeitem{EggPlug,\\ NAS and Cloud Storage}{EggPlug (www.eggplug.com) is a physical device which lets you access your digital media across the Internet. Contents across various other Physical plugs and desktop installations are kept in sync. User selected files/folders are backed incrementally onto Amazon S3. Devices are authenticated using OAuth protocol. One could simply consider this product as a NAS and Dropbox solutions combined. EggPlug can automatically backup your most important folders to EggRack,the Cloud based, versioned backup service.}
\largeskip

\resumeitem{Cyclozzo,\\ PaaS}{Cyclozzo is a meta cloud platform designed to support the latest PaaS APIs with minimal effort. Cyclozzo currently implements two of the most popular PaaS APIs: Google App Engine Python and Google App Engine Java. Cyclozzo continuously monitors application requests and makes sure that user applications are responsive at all times, while utilizing optimal server resources. When load goes up, Cyclozzo increases the number of application instances and also decreases them when requests come down. Cyclozzo does auto scale-out and scale-in while taking in to account the application's budget/plan.}
\largeskip

\resumeitem{ScaleInfra,\\ Scalability Manager}{ScaleInfra is yet another infrastructure management tool. ScaleInfra can deploy customer applications based on their requirements in a public/private infrastructure deployment. It uses FluidVM/AmazonEC2 for private/public deployments. ScaleInfra employs layer-based strategy to categories virtual machines (like external world visibility). Virtual machines in a layer is pre-configured to a Linux XenPV template. There is an additional option to associate shell scripts per template. Layers are configurable. Application scalability is done by increasing and decreasing the number of virtual machines participating in the application cluster.}
\largeskip

\resumeitem{Pyles,\\ Python Framework}{Python application development was our primary goal and there were some features, which we used on a regular basis at  K7 Computing. Pyles was developed to reduce application development time. The main purpose of this framework was to provide a web interface using a web serverand database schema migration capability. Pyles supports few open-source databases like MySQL and SQLite. Other features include automatic validation based
on pre-build values/range dictionary, task queue, simple calls for save, update and delete functionalities,Multiple dynamic user roles, cookie based authentication, pre and post start procedures etc.}
\largeskip

\resumeitem{MCNHRMS,\\ Human Resource Management Portal}{MCN is an HR services and placement providing organization aligned to address the objective to obtainthe efficiencies and effectiveness of IT power processes. MCNHRMS is an Intranet Workflow Management portal. This Portal usage is for authorized MCN employeesonly. This Portal enables the authorized users to capture the market details, specific client requirements, allocate the requirements to the consultants, fulfil the requirements and complete the formalities of the closure of the requirement. The individual credits and performance monitoring and their Key Result Areas tracking will be done only through this portal. Delivery Lead allocates client's requirements to consultant. Consultant sends all clients requirement to QCperson and also manages the candidate recruitment process. Associate consultant updates the candidate feedback status sent by the client. Quality Checker (QC)Understands client requirements and performs QC.}
\largeskip

\resumeitem{Island-worldwide,\\ Online Travel agency}{I-W provides leisure and business travellers a wide selection of low airfares, as well as deals on lodging, car rentals, cruises, vacation packages and other travel. It is to address consumer's need for an unbiased, comprehensive display of fares and rates in a single location. Its inventory includes hundreds of airlines, more than 80,000 hotels worldwide and 13 rental car brands. Search results are presented in an easy-to-use matrix that displays a vast array of travel options.}
\largeskip

\resumeitem{ACAPS,\\ Online financing solution product}{Automatic Credit Application Processing System is an online financing solution product. ACAPS can helpa customer, who finds paying off debts, difficult. The product also gives homeowners an option to borrow against their equity to pay off their debts in full. This could be accomplished, even if they have been denied a loan by other lenders. Once the customers consolidate all their monthly debt into one lower payment, they can breathe easier. Interest on their new monthly payment may even be tax-deductible. Plus, they can arrange to have cash left over to spend as they wish. And unlike other lenders, the customer can prequalify in as little as 24 hours and deliver their funds in days, not months.}
\newline
\largeskip
\end{resumeblock}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{resumeblock}{Online Profile}

\resumeitem{LinkedIn}{in.linkedin.com/in/RJKarthickRaj}
\newline
\largeskip

\end{resumeblock}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{interestsblock}{Interests \& Activities}
    \\
	\interest{idea}{Learning new technologies} &
	\interest{Cam}{Photography}\\
	&\\
	\interest{Travel}{Travel} &
	\interest{Music}{Music} 
\end{interestsblock}

\end{document}
